### 2016-08-23 notions.tex
trying to sort out privacy notions, post-crypto chat

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a
set-representation.   There are various ways to formalize privacy, and
we give some of these in Figure~\ref{fig:privacy}.  
%\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
%to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
%If $S$ has high min-entropy (element-wise), then it might still be
%possible to have security here.}\tsnote{I think we will always bump up
%against the (element-wise) min-entropy of the distribution over~$S$,
%at least in the ``one-wayness'' style definition that I had been imagining. }
On the left side of this figure, we give two ``one-wayness''
definitions, in which the adversary must output an element of the
set~$S$ represented by~$M$.  The first version (priv) gives the
adversary~$(M,\pubaux)$ as input; the second (wpriv) gives
only~$\pubaux$.  The wpriv-notion captures leakage about the elements
of~$S$ that results from observing the results of allowed queries.
The stronger priv-notion captures what is jointly leaked, by the
representation~$M$ and the allowed queries, about set elements.

%On the right side of the figure, we give two ``indistinguishability''
%notions of privacy.  The first version (ind-qry) captures more
%generally what~$M$ and the allowed queries leak about the set that is
%represented.  In particular, two sets~$S_0,S_1$ are sampled according
%to distribution~$\distr{\calS}{}$, one of these is picked at random to
%be represented.  The adversary is provided the resulting~$M,\pubaux$
%and allowed to make queries~$q \in \calQ$; it must determine which
%of~$S_0$ or~$S_1$ was actually represented.  We call this notion
%indistinguishabilty (of sets) under a (adaptively chosen) query
%attack.
%
On the right side of the figure, we give a definition
inspired by the semantic security notion for
encryption schemes.  We refer to it as semantic-security (of sets)
with respect to the full representation (ss-rep).  In this experiment,
a set~$\calS$ is sample according to distribution~$\distr{\calS}{}$,
and the adversary is given the full ouput of running $\Rep(S)$,
i.e. $(M,\pubaux,\privaux)$.  The adversary must output a
function~$f\colon\calS \to \bits^*$ such that $f(S)$ differs from
$f(S')$ for a set~$S'$ that is subsequently sampled according to~$\distr{\calS}{}$.

\if{0}
There are several possible definitions:
\begin{enumerate}
\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
give the attacker $\pubaux$ and either $M$ or oracle access to $\Qry$. The attacker
succeeds if it can output an element in~$S$. \tsnote{fixed by
  changing syntax.}\tsnote{Neither of these seems to capture the Neidermeier et al. attack.  Giving the adversary~$M$ is closest, but our syntax would put the hash function secret keys into~$M$, which the Neidermeier attack doesn't get.}

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\pubaux$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
  This says that security is required \emph{only} for properties that are
  true of both sets.  So a scheme with $M=S$ will be trivially secure
  against set membership queries.  Maybe we restrict from queries~$q$ that are a priori known to have the same value for all sets~$S \in \calS$, or all~$S$ of a given size, etc., as these might be pointless?)}

\tsnote{Is this the right kind of indistinguishability anyway?  This
  current notion says, in effect, that $S_0$ and $S_1$ are
  indistinguishable \emph{with respect to the allowed queries}
  (assuming that $\pubaux$ doesn't stupidly leak information.)  But
  why not try to formalize the intution that a representation~$M$ and
  the public info~$\pubaux$ tell you nothing (non-trivial) about the
  set being represented, period?  (Classical BFs, by the way,
  essentially leak the number of elements in the set by looking at the
  number of 0-bits in the array.)   That's tricky to define... I'll
  take a shot at it.}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}
\fi

\begin{figure}[htbp]
\centering
\hfpages{.495}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(M,\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.485}{.5}
{
%\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
%$b \getsr \bits$\\
%$S_0,S_1 \getsr \distr{\calS}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
%$b' \getsr A^{\TestOracle}(M,\pubaux)$\\
%if $b' = b$ then Return 1\\
%Return 0\\
%
%\medskip
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
$S\getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$f \getsr A(M,\pubaux,\privaux)$\\
$S' \getsr \distr{\calS}{}$\\
if $f(S) \neq f(S')$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$\\

%\medskip
%\oracle{$\RepOracle(S_0,S_1)$}\\
%if $\mathrm{used}=\true$ then Return $\bot$\\
%%if $|S_0|\neq|S_1|$ then \\
%%\nudge Ret $\bot$\\
%$S_0,S_1 \getsr \distr{\calS}{}$\\
%$\mathrm{used}=\true$\\
%$(M,\aux) \getsr \Rep(S_b)$\\
%Return $(S_0,S_1,\aux)$\\

}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The bottom is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion and a semantic-security style notion. (Still playing...)} 
\label{fig:privacy}
\end{figure}

\subsection{Relationships Among Notions}

>>>>

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a
set-representation.  We formalize two types of privacy notions. One
type captures a kind of one-wayness of the representation~$M$,
relative to the allowed queries.  Informally, that given the
representation and the public information, it is hard to guess any
value in the represented set~$S$.  The other type captures a kind of
semantic security, essentially requiring that $(M,\pub)$ and th
allowed queries do not leak any (non-trivial) information about the set~$S$.
%\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
%to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
%If $S$ has high min-entropy (element-wise), then it might still be
%possible to have security here.}\tsnote{I think we will always bump up
%against the (element-wise) min-entropy of the distribution over~$S$,
%at least in the ``one-wayness'' style definition that I had been imagining. }

In Figure~\ref{fig:privacy-ow} we give two ``one-wayness''
definitions, in which the adversary must output an element of the
set~$S$ represented by~$M$.  The first version (priv) gives the
adversary~$(M,\pubaux)$ as input; the second (wpriv) gives
only~$\pubaux$.  The wpriv-notion captures leakage about the elements
of~$S$ that results from observing the results of allowed queries.
The stronger priv-notion captures what is jointly leaked, by the
representation~$M$ and the allowed queries, about set elements.  We
define advantage measures $\AdvPriv{\Pi,\distr{\calS}{}}{A} =
\Prob{\ExpPriv{\Pi,\distr{\calS}{}}{A}=1}$ and $\AdvWPriv{\Pi,\distr{\calS}{}}{A} =
\Prob{\ExpWPriv{\Pi,\distr{\calS}{}}{A}=1}$; in both we track the
time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.

\tsnote{Still messing about here, and in the figure.}
In Figure~\ref{fig:privacy-ss} we give a definition capturing semantic-security (of sets)
with respect to the full representation (ss-rep).  In the ``real''
setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{\calS}{}$,
and the adversary is given the~$M,\pubaux$ that result from running
$\Rep(S)$.  It is also provided oracle access to $\QryOracle$.
The adversary must output a function~$f\colon\calS \to \bits^*$ and a
string~$v$ such that $f(S)=v$.  In the ``fake'' setting (ss-rep-0) a
predictor~$P$ is given $\pubaux$ only, and no $\QryOracle$ access.  It
also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
is $\AdvPrivSS{\Pi,\distr{\calS}{}}{A,P} =
\Prob{\ExpPrivSSreal{\Pi,\distr{\calS}{}}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,\distr{\calS}{}}{P}=1}$.  To prevent trivial wins
for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
such that $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{\calS}{}$.

\begin{figure}[htbp]
\centering
\fpage{.495}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(M,\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$
}
}
\caption{``One-wayness'' style privacy
  definitions. The bottom is a weaker notion, because the representation
  is hidden from the adversary.} 
\label{fig:privacy-ow}
\end{figure}

%
\begin{figure}[htbp]
\centering
\hfpages{.495}
{
\hpagess{.49}{.49}
{

\experimentv{$\ExpPrivSSreal{\setprim,\distr{\calS}{}}{A}$}\\
$S\getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(f,v) \getsr A^{\TestOracle}(M,\pubaux)$\\
if $f(S)=v$ then\\
\nudge Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
$S\getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(f,v) \getsr P(\pubaux)$\\
if $f(S)=v$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
{
\hpagess{.49}{.49}
{
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{},P}{A}$}\\
$S\getsr \distr{\calS}{}$\\
$b \getsr \bits$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
$M_0 \getsr P(\pubaux)$\\
%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
%if $f(S)=v$ then\\
if $b'=b$ then\\
\nudge Return 1\\
Return 0\\
%
%\medskip
%\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
%$S\getsr \distr{\calS}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(f,v) \getsr P(\pubaux)$\\
%if $f(S)=v$ then\\
%\nudge Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
\caption{Semantic-security style privacy definitions. } 
\label{fig:privacy-ss}
\end{figure}
\subsection{Relationships Among Notions}
